---
title: "Movie Analysis Report"
author: "Malay Raj"
date: "2023-05-27"
output:
  word_document: default
  html_document: default
---

## MOVIES DATASET ANALYSIS:

Movies Dataset (made available by Rounak Banik under a CC0 license): Metadata about 45,000 movies, with data points
including cast, crew, plot keywords, budget, revenue, ratings, release dates, languages, production companies, and more.

## Loading Required Packages.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plyr)
library(skimr)
library(readxl)
```


## Displaying my current working directory.

```{r}
getwd()
```

## Collecting the data.

```{r}
movies = read_excel("C:/Movies Analysis/movies_data.xlsx")
```

## Displaying the first six rows of the dataset.

```{r}
head(movies)
```

## Checking the number of rows and dimension of the dataset.

```{r}
nrow(movies)

dim(movies)
```

## Renaming few columns.

```{r}
movies=plyr::rename(movies, replace=c( "genres...5" = "Genres",
                                       "title"="movies_title",
                                       "id"="movies_id"))
```


## Viewing the new column names.

```{r}
colnames(movies)
```


## Inspecting the dataframe and look for inconguencies.

```{r}
str(movies)
```

# Convert  release_year to numeric datatype so that they can stack correctly.

```{r}
movies$release_year = as.numeric(movies$release_year)
```

## Inspecting the dataframe after changing the datatypes.

```{r}
str(movies)
```


## Removing few columns because we don't need it in our analysis.

```{r}
movies = subset(movies, select = -c(genres...4, production_countries, release_date))
```


## Viewing all the column left after removing the columns.

```{r}
colnames(movies)
```


## Checking for null values in our dataset.

```{r}
sum(is.null(movies))
```


## Checking for any duplicate values in our dataset.

```{r}
anyDuplicated(movies)
```

Removing the duplicate values from our dataset.

```{r}
movies1 <- unique(movies)
```


Now checking for the duplicate values again.

```{r}
anyDuplicated(movies1)
```


## Seeing how many observations fall under each of these columns.

```{r}
table(movies$Genres)
table(movies$countries)
table(movies$original_language)
table(movies$release_year)
```


## CONDUCTNG DESCRIPTIVE ANALYSIS:

Descriptive analysis on few columns.

```{r}
summary(movies1$budget)
```


```{r}
summary(movies1$revenue)
```


```{r}
summary(movies1$vote_average)
```


```{r}
summary(movies1$vote_count)
```


Comparing vote_count, vote_average with different Genres.

```{r}
aggregate(movies1$vote_count ~ movies1$Genres, FUN = mean)
aggregate(movies1$vote_count ~ movies1$Genres, FUN = median)
aggregate(movies1$vote_count ~ movies1$Genres, FUN = max)
aggregate(movies1$vote_count ~ movies1$Genres, FUN = min)
```

```{r}
aggregate(movies1$vote_average ~ movies1$Genres, FUN = mean)
aggregate(movies1$vote_average ~ movies1$Genres, FUN = median)
aggregate(movies1$vote_average ~ movies1$Genres, FUN = max)
aggregate(movies1$vote_average ~ movies1$Genres, FUN = min)
```


## SUMMARY STATISTICS.

```{r}
skimr::skim_without_charts(movies1)
```


As we can see there are few missing values in runtime column.

```{r}
movies1 <- movies1 %>% drop_na(runtime)
```


Again using the same code to check if the missing values are dropped or not.

```{r}
skimr::skim_without_charts(movies1)
```


## Checking the dimension of the dataframe after deleting columns and dropping missing values.

```{r}
dim(movies1) 
```


## DATA VISUALIZATION:

Checking the number of votes per Genre.

```{r}
ggplot(movies1) + 
  geom_col(mapping = aes(x=Genres, y=vote_count, fill=Genres)) + 
  coord_flip() +
  labs(title="Votes Per Genre") 
```


Checking number of votes with different status.

```{r}
ggplot(movies1) + 
  geom_col(mapping = aes(x=status, y=vote_count)) + 
  labs(title="Status Votes")
```


Checking for the number of votes per Genre.

```{r}
ggplot(movies1) + 
  geom_col(mapping = aes(x=release_year, y=vote_count)) + 
  labs(title="Votes Per Genre")
```


Checking the Top 10 movies popularity vise.

```{r}
movies1 %>%
  arrange(-popularity) %>%
  slice_head(n=10) %>%
  ggplot(aes(reorder(movies_title, popularity), popularity)) +
  geom_point(colour = "blue", size = 3) +
  theme(text=element_text(size=10)) + 
  coord_flip() +
  labs(title = "Top 10 most popular movies of all time", x = "")
```


Checking for the Top 10 most voted movies.

```{r}
movies1 %>%
  arrange(-vote_count) %>%
  slice_head(n=10) %>%
  ggplot(aes(reorder(movies_title, vote_count), vote_count)) +
  geom_point(colour = "blue", size = 3) +
  theme(text=element_text(size=10)) + 
  coord_flip() +
  labs(title = "Top 10 most voted movies of all times", x = "")
```


Checking the most popular Genres.

```{r}
ggplot(movies1 , aes(x = Genres, y = popularity)) +
  geom_boxplot(aes(fill=Genres)) + theme_bw() +
  theme(axis.text.x = element_text (angle = 90))
```


Checking for the Top 10 highest revenue generated movies of all time.

```{r}
movies1 %>%
  arrange(-revenue) %>%
  slice_head(n=10) %>%
  ggplot(aes(reorder(Genres, revenue), revenue)) +
  geom_point(colour = "blue", size = 3) +
  theme(text=element_text(size=10)) + 
  scale_y_continuous(labels=scales::dollar_format()) +
  coord_flip() +
  labs(title = "Top 10 most revenue generated movies of all times", x = "")
```


Checking for the most revenue generated Genres.

```{r}
movies1 %>%
  ggplot(aes(x=Genres, y=revenue)) +
  geom_col(fill='blue') +
  coord_flip() +
  scale_y_continuous(labels=scales::dollar_format()) +
  labs(title="Most revenue generated genres")
```


